\section{Introduction}

\subsection{Introduction}
In Data4Help implementation and testing document the process of the system creation from the backend to the frontend is analyzed. Before continuing the reading of this document it is highly suggested to read the RASD and the DD to better acknowledge the development decisions.
Data4Help is a service strongly based on the server side, whereas the apps for the users are used to access 
the services provided by the system.
This will be a key feature to keep in mind in order to better understand the ordering of feature implementations and so on.

\subsection{Scope}
The scope of this document is to provide a general overview of the structure of the code, while referring mainly to the DD for the code design and testing decisions, and the RASD for the features implemented.
Regarding the features implemented, the document will go deep in details in explaining what are the features implemented and why some features where dropped during the development of Data4Help.
Moreover a guide to successfully install the app, and starting the server will be provided with insights on their user interfaces and functionalities.


\subsection{Acronyms}

\begin{itemize}
\item \textbf{API}: Application programming interface
\item \textbf{DD}: Design Document
\item \textbf{DB}: Database
\item \textbf{EJB}: Enterprise JavaBeans
\item \textbf{RASD}: Requirements Analysis and Specifications Document
\item \textbf{REST}:Representational State Transfer
\end{itemize}


\subsection{Abbreviations}
\begin{itemize}
\item[Rn]: n-th functional requirement
\end{itemize}

\subsection{Document Structure}

The ITD is structured in the following way:
it starts with a brief of description of the document and an introduction in Chapter 1.

\bigskip\noindent
Chapter 2 is focused on the requirements implemented: in this chapter there is a general description of the decision made during development and how and where the requirements are realized in the source code.

\bigskip\noindent
Chapter 3 presents the frameworks used during development.

\bigskip\noindent
Chapter 4 has a general overview of the source code structure.

\bigskip\noindent
Chapter 5 describes the testing process used for Data4Help components.

\bigskip\noindent
Chapter 6 presents the installation instructions for both the Server and the Android App.

\bigskip\noindent
Chapter 7 contains the references cited in the document.

\bigskip\noindent
Chapter 8 show the effort spent by each group member in order to realize the ITD document and Data4Help system.